Beyond the Numbers: Dissecting New York City's Leading Causes of Death Across Demographics

### 2024-03-15 paper/paper.qmd
rendered paper to latest versio

>>>>

In our research, we investigated the causes of mortality within New York City’s diverse racial and ethnic populations for the year 2014. We hypothesize that the total number of deaths by leading cause follows a negative binomial regression. 
Formally, the model is expressed as:
$y_i | n_i \sim \text{NegBin}(\mu_i, k)$

In the expression above, $y_i$, signifies the count of deaths for cause i,$\mu_i$ is the expected count, and $k$ is the dispersion parameter, which captures over-dispersion. 
Our model also utilizes a log-link function, modeling the expected log-count as:
$\log(\mu_i) = \beta_0 + \beta_1 \times \text{Cause}_i$

Where $\beta_0$ is the intercept, and $\beta_1$ represents the vector of coefficients for the leading causes of death. 
The leading causes are treated as categorical predictors, which results in the need to use dummy coding with one reference category.

For our Bayesian regression framework, we employ the stan_glm() function from the rstanarm package, which assumes default normal priors for the regression coefficients as follows:
$\beta_0$ ~ Normal(0,2.5)
$\beta_1$ ~ Normal(0,2.5)
